The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-21 paper/ms.tex
Figure Size labels
new subsection describing the radiative transfer codes

Additionally, we have used two independently developed Monte Carlo
codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report are robust in the sense
that they are obtained by both codes.

@@

@@

\subsection{Off-Centered emission}
\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

>>>>

Additionally, we have used two independently developed Monte Carlo
codes \cite{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report are robust in the sense
that they are obtained by both codes.

@@

\subsection{Brief Description of the Radiative Transfer Codes}

Here we briefly describe the relevant points for the two radiative
transfer codes we have used. For a detailed description we refer the
reader to the original papers \cite{CLARA,DijkstraKramer}.

The codes follow the individual scatterings of \ly photons as it
travels through a 3D distribution of neutral Hydrogen. At each
scattering the frequency of the photon (in the laboratory frame) and
its direction of propagation change. This change in frequency is due
to the peculiar velocities of the Hydrogen atom that absorbed and
reemitted the photon. If dust is present, the photon can interact
either with a Hydrogen atom or dust grain. In the case of a dust
interaction the photon can be either absorbed or scattered, this
probability is encoded in the dust albedo, $A$, which we chose to be
$1/2$. In order to obtain accurate values for the escape fraction of
photons in the presence of dust, we do not use any accelerating
mechanism in the radiative transfer.  Once the photons escape the gas
distribution we store their direction at their direction of
propagation and frequency at their last scattering.

The photons are thus emitted in some region of the gas distribution
and follow a random walk in space and frequency until they escape the
gas distribution or are absorbed by a dust grain. The initialization
process for the \ly photons has to specify its position, frequency and
direction of propagation. In our case we select the initial frequency
to be exactly the \ly restframe frequency ($x=0$) and the direction of
propagation to be random following an flat probability distribution
over the sphere.

The gas is completely defined by its geometry (i.e. sphere or slab),
temperature $T$, Hydrogen optical depth $\tau_{\rm H}$, dust optical
depth $\tau_{\rm a}$ and the bulk velocity field $\vec{v}$.  Here we
treat the gas as homogeneous in density ($\tau_{\rm H}$, $\tau_{\rm
  a}$) and temperature.

@@

\subsection{Off-Centered emission}
\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}
